### 2022-06-14 main/chapter_2ljets.tex
write offshell region section

\FloatBarrier
\subsection{Off-shell}
\label{sec:2ljets_offshell}
Table~\ref{tab:2ljets_offshell}
Figure~\ref{fig:2ljets_offshell_region}

@@

@@

>>>>

\FloatBarrier
\subsection{Off-shell}
\label{sec:2ljets_offshell}
Previous iterations of our $\twoljets$ search did not target `off-shell'
scenarios~\cite{atlas_23l_SUSY_2016_24, atlas_2l_SUSY_2013_11}, in which
models have mass splittings below $m(W)$ or $m(Z)$, such that decays must
proceed below their pole masses.
Models with smaller off-shell mass splittings are described as more
`compressed'.
Separate searches have, however, targetted compressed scenarios in
specialized and carefully designed analyses~\cite{
atlas_susy_compressed_2l_2016_partial_run2,
atlas_susy_compressed_2l_2018_run2
} in selections with two leptons.

Since compressed signals generate softer kinematics and \atlas\ is sensitive
to soft leptons, three-lepton searches have stronger sensitivity to
compressed scenarios~\cite{atlas_rjr_3l_SUSY_2019_09}.
These searches consider the same C1N2 $WZ$ signal models as us, but target the
case where the $W$ decays leptonically $W\rightarrow\ell\nu$.
For comparison, impressive off-shell exclusion contours are reproduced
from the \atlas\ Run-2 $3\ell$ search~\cite{atlas_rjr_3l_SUSY_2019_09} in
Figure~\ref{fig:ljets_offshell_3l_exclusion}.

\begin{figure}[tp]
\centering
\includegraphics[width=0.9\textwidth]{figures/2ljets_compressed_3l_ins1866951_fig_16a.png}
\caption[
Contours showing off-shell C1N2 exclusion from the \atlas\ Run-2 $3\ell$ search
]{%
Contours showing off-shell C1N2 exclusion in the three lepton channel,
reproduced from the \atlas\ Run-2 $3\ell$
search~\cite{atlas_rjr_3l_SUSY_2019_09, hepdata.95751}.
Off-shell models are excluded in that large lobe squeezed between the
$m(\neutralino_2) = m(\neutralino_1)$ and
$m(\neutralino_2) = m(\neutralino_1) - m_Z$ diagonal lines.
}
\label{fig:ljets_offshell_3l_exclusion}
\end{figure}

Despite the expert input from these off-shell and compressed searches, it was
decided that $\twoljets$-electroweak should chime in to the off-shell
conversation.
Although specialized searches benefit from softer leptons and $\met$
triggers~\cite{atlas_susy_compressed_2l_2018_run2},
we still have some sensitivity since standard model backgrounds drop off
below $\mll \approx m(Z)$.

This is the purpose of SR-OffShell and its associated validation and control
regions that are defined in Table~\ref{tab:2ljets_offshell}.
Histograms of SR-OffShell and VR-OffShell are displayed in
Figure~\ref{fig:2ljets_offshell_region}, and the off-shell control region
CR-DY is displayed in Figure~\ref{fig:2ljets_offshell_cr_region}.

@@

Our off-shell regime is characterized by $\mll < m(Z)$.
The $W$ must also be off shell, the softer hadronic activity from light $W^*$
events is not reliably reconstructed as signal jets.

Early OffShell designs used the `ISR' construction, which is described
Section~\ref{sec:2ljets_low} for Low regions,
and which seeks hard jets which boost the supersymmetric particles and their
decay products.

After some iterations, however, the same intent was reproduced with a simpler
and more effective selection.
As seen in Table~\ref{tab:2ljets_offshell}, this design is to simply ask for
one hard jet facing away from $\ptmiss$; this is specified as
$\ptjone > 100\,\eV[G]$ and $\dphijmet > 2$.
In comparison to ISR variables, this design improves yields by not needing jets
for a $W\rightarrow jj$ candidate.

An upper limit of $\mjj < 71\,\eV[G]$ is chosen for orthogonality from all
on-shell regions.
Our simulations of $\zjets$ are split into on- and off-shell parts at
$40\,\eV[G]$, so that forms a natural breakpoint for binning which might help
to separate concerns about systematic variations.
As always, this binning aids sensitivity since models' contributions to the
the bins vary with their mass splittings.

Hadronic resonances which decay to lepton pairs,
such as the bottomonium $\Upsilon$,
become important below $10\,\eV[G]$, and we did not have simulations available
for the $\mll < 10\,\eV[G]$ range.
The requirement $\mll > 12\,\eV[G]$ is therefore imposed to robustly remove
this un-modelled regime with a margin for error.

Unlike on-shell regions, the standard $\mttwoll > 80\,\eV[G]$ requirement did
not adequately reduce off-shell $\ttbar$ backgrounds.
Pushing it up to $\mttwoll > 100\,\eV[G]$ was found to work well for the signal
region, and the $\mttwoll \in 80\textrm{--}100\,\eV[G]$ nicely forms a the
nearby validation region.
Part of the light $\mll$ background arises from leptonically decaying
$Z\rightarrow \tau\tau$ events; these are also removed by requiring large
$\mttwoll$.

Away from the $m(Z)$ peak, the full dilepton spectrum is not dominated by the
$Z$ resonance, but depends on the full Drell-Yan, $\zyjets$,
process~\cite{drell1970massive}.
That is, on- and off-shell $\mll$ distributions are physically different.
Since also $\zyjets$ simulations are culturally not trusted, we decided
to introduce separate normalization factors for $\zyjets$ in on- and off-shell
regions.

@@

The control region CR-DY (named after Drell and Yan) is defined to normalize off-shell $\zyjets$ near to
SR-OffShell.
Its reduced $\metsig$ requirement and relaxed angular selections were required
to increase yields.
As seen in Figure~\ref{fig:2ljets_offshell_cr_region}, pre-fit backgrounds
agree well with data.
Contributions of $\zyjets$ in SR-OffShell are small anyway, as shown in
Figure~\ref{fig:2ljets_offshell_region}.
